
Convergence - use the optimal afforded strategies ---- in convergent environments form and function is stabilized to a higher degree. This doesn't allow for radical changes and alternatives. 

Cost-benefit analysis. What is a benefit! What is a cost!

Chunking: Short-term memory 4 +/- 1
Closure: Fill in missing space
Color: Matching, Symbolic, Saturation, Numbers
Common fate: Objects are linked when moving together at similar speeds.
Cognitive dissonance: Struggle with holding two opposing ideas and being consistent.
Consistency: Aesthetic, Functional, Internal/External
Depth processing: Recall is easier for information presented with distinctiveness, relevance and a high degree of elaboration
Expectation effects: Expectations effect behaviour and perception, both physically and psychologically. Probable - desired outcomes
Exposure effects: repeated exposure to an indifferent variable can raise likeability.
Feedback-loops: Positive/Negative - Consequences of an event feedback into a system
Highlighting: Bringing attention to certain areas by visual qualities
Layering: Organizing information into groups, to manage complexity
Mapping: Relationship between control and movements, closer to expectation is better
Mental model: The mental idea of how something works
Mimicry: The act of copying properties in order to draw a relation and benefit from the properties afforded 
Modularity: Managing system complexity by dividing larger system into smaller -
Nudge: Changing perception without restricting options or significantly changing incentives
 
Ockham's Razor: Given two equal choices the simplest explaination or choice is superioer
Operant conditioning: Increasing/Decreasing a behaviour by associating it with a positive or negative condition
Performance load: The greater the effort to accomplish a task the higher the chance the task will fail
Performance vs Preference: Choice depends upon preference not arbitrary measures such as performance
Pictorial superiority effect: Pictures are remembered better than words
Progressive disclosure: Managing information complexity by only showing requested or neccessary information
Proximity: Elements closer together are perceived to be more related than elements further apart
Recognition over recall: Memory for recognizing things is better than for recalling things.
Saticifying: Settling for satisfactory over struggling for optimal solutions
Signal-to-noise ration: The ratio of relevant to irrelevant information in a display
Similarity: Items that appear similar are perceived to be more related
Storytelling: Setting, Character, Plot, Invisibility, Mood, Movement.
Uniform connectedness: 


``Make all visual distinctions as subtle as possible, but still clear and effective''tufte-visualexplainations-p.73
