\documentclass[11pt,UKenglish, a4paper]{article}
\usepackage[utf8]{inputenc}
%--fonts--
\usepackage[T1]{fontenc}
\usepackage[bitstream-charter]{mathdesign}

%--packages--
\usepackage[UKenglish]{babel}
\usepackage{csquotes,textcomp,varioref}

\usepackage{graphicx}
%--color--
\usepackage[dvipsnames]{xcolor}

%Setter inn pdfer
\usepackage[final]{pdfpages}

%-linespace--
\linespread{1.3}

%--hyperlinks-- include 
\usepackage[colorlinks=false, pdfborder={0 0 0}]{hyperref}

%--Endrer på enumerate lister
\usepackage{enumitem}


%--fullpage--
%\usepackage{fullpage}

%--Uio-Front-Page--
%removed until it works \usepackage{ifikompendiumforside}

%--bibliography- -sortlocale=nb_No,
\usepackage[backend=biber, sortcites, defernumbers, style=numeric-comp, maxnames=2, natbib=true, backref, sorting=none, url=false]{biblatex}
%fjernet ifra style=authoryear-icomp

%farger jeg skal ha med
\definecolor{myY}{RGB}{241, 196, 15}
\definecolor{myB}{RGB}{52, 152, 219}
\definecolor{myG}{RGB}{46, 204, 113}
\definecolor{myLy}{RGB}{149, 165, 166}
\definecolor{myR}{rgb}{231, 76, 60}

%--Author and Title--
\author{Simon Lysne Hyenes}
\title{Overview of master}


%--Latex Optimalization--
\tolerance = 5000
\hbadness = \tolerance
\pretolerance = 2000

%---------start------------
\begin{document}

\maketitle{}
\section{Introduction}
This document contains the current plan for my master thesis.

\section{Chapter 1. Introduction}
\begin{enumerate}
\item \textbf{Kulu}
\item \textbf{Motivation}
\item \textbf{Reseach questions}
\end{enumerate}

\section{Chapter 2. Literature review}
\begin{enumerate}[label=\bfseries\arabic*]
\item \textbf{Criteria}\hfill \\
What literature have i included

\item \textbf{Theoretical Framework}
	\begin{enumerate}[label=\bfseries\arabic*]
	\item Time
	\item Visualization
	\item Mastery
	\end{enumerate}
\end{enumerate}

\section{Chapter 3. Ethics}
\begin{enumerate}[label=\bfseries\arabic*]
\item \textbf{Research with younger teens and patients} \hfill \\
KULU, raised ethical concerns
\item \textbf{Wicked Problems} \hfill \\
How can we frame problem situations
\item \textbf{Ethical framework} \hfill \\
Reworked framework. 
\item \textbf{Designers / Researcher role} \hfill \\
Framing and forming futures
\item \textbf{Teenagers and patients} \hfill \\
Concerns directly linked to working with underrepresented groups. Extra legal rules and guidelines. Research ethics. 
\end{enumerate}

\section{Chapter 4. Conceptual framework}
\begin{enumerate}[label=\bfseries\arabic*]

\item \textbf{Time}\hfill \\
Time and culture

Classifying time

Timelines as mental models

Monochronicity/Polychronicity

Personal relation to time.
Benefit of being framed towards future-positive. Future-positive as an inclination towards the future. Not making decision entirely based on past or present experiences and needs.
\item \textbf{Design for mastery} \hfill \\
What is the theory of mastery

Design for mastery
\item \textbf{Visualization}
	\begin{enumerate}[label=\bfseries\arabic*]
		\item \textbf{Timelines} \hfill \\
		How is time visualized, alternatives and implications.
		\item \textbf{Art and design} \hfill \\
		What is the relation for visualization between art, data representation and presenting realities.
		\item \textbf{Narratives} \hfill \\
		Can timelines be narrative tools. What type of narratives can they tell. 

		Social media, facebook timeline.

		Can timelines be diaries.
		\item \textbf{Cool} \hfill \\
		What visualizations speak to the user group. Should \textit{cool} be a factor. 
		\item \textbf{Meaningful data} \hfill \\
		What is not meaningful. 
	
		What data-types are there: quantified - qualitative - other

		Rules and standards
	
		Application

		Actionable data: For whom. 
		\item \textbf{False realities} \hfill \\
		Problems with visualization and false narratives. 

		De-constructing and restructing data.

		Seeing patterns in noise versus seeing only noise in patterns.

		\end{enumerate}
		\end{enumerate}

\section{Chapter 5. Methodological framework}
\begin{enumerate}[label=\bfseries\arabic*]
\item \textbf{Research paradigm}\hfill \\
Short about qualitive research. If neccessary.
\item \textbf{Participatory design}\hfill \\
	Short introduction about participatory design
	\begin{enumerate}[label=\bfseries\arabic*]
	\item Why use PD
	\item Ethical considerations
	\item Scope for this project\hfill \\
	Explain the limitations and why this cannot be considered a PD-project. Instead that we are drawing upon PD for a more informed approach.
	\end{enumerate}
	\item \textbf{Design cycle}
	\item \textbf{Methods}
		\begin{enumerate}[label=\bfseries\arabic*]
		\item Participatory methods
		\item Choice of methods
			\begin{enumerate}[label=\bfseries\arabic*]
			\item Participatory sketching
			\item Semi-structured interview
			\end{enumerate}
		\end{enumerate}
\end{enumerate}

\section{Chapter 6. Data Collection}
\begin{enumerate}[label=\bfseries\arabic*]
\item \textbf{Workshop 1}
	\begin{enumerate}[label=\bfseries\arabic*]
	\item Preparation
	\item Setting
	\item Structure
	\item Reflection
	\end{enumerate}
\item \textbf{Between the workshops}
\item \textbf{Workshop 2}
\item \textbf{Reflection} \hfill \\
Issues

Dynamics

Expectations versus results
\end{enumerate}

\section{Chapter 7. Data and analysis}
\begin{enumerate}[label=\bfseries\arabic*]
\item \textbf{Workshop 1}
	\begin{enumerate}[label=\bfseries\arabic*]
	\item Thematic analysis
	\item Results
	\item Further work
	\item Discussion
	\end{enumerate}
	\item \textbf{Workshop 2}
	\begin{enumerate}[label=\bfseries\arabic*]
	\item Analysis
	\item Results
	\item Discussion
	\end{enumerate}
\end{enumerate}

\section{Chapter 8. Design proposal}
\begin{enumerate}
\item \textbf{Prototyping}
\end{enumerate}

\section{Chapter 9. Evaluation of design and research process}
\begin{enumerate}
\item Methodology
\item Methods
\item Participatory design
\item Scope
\item Data collection
\item Reflection
\end{enumerate}

\section{Chapter 10. Conclusion}
\begin{enumerate}
\item \textbf{Reflection}
\item \textbf{Further work}
\end{enumerate}


\end{document}

